ms_8

### 2020-04-27 ms_8.Rmd
almost finished food access tab

# Read in rural income data from
# https://www.ers.usda.gov/data-products/atlas-of-rural-and-small-town-america/
# (United States Department of Agriculture)

@@

# Read in income data for all US Counties from
# https://www.ers.usda.gov/data-products/county-level-data-sets/download-data/
# (US Bureau of Labour Statistics)

@@

# REad in consumer Price Index ata from
# https://www.ers.usda.gov/data-products/food-price-outlook/ (United States
# Department of Agriculture)

@@

anim_save("plots/obesity_mean_usmap.gif", plot = last_animation())

@@

ggsave("plots/obesity_region_plot.png", plot = last_plot())

@@

ggsave("plots/food_poverty_plot.png", plot = last_plot())

@@

ggsave("plots/food_lia_plot.png", plot = last_plot())

@@

@@

ggsave("plots/corr_plot.png", plot = corrplot)

@@

@@

@@

@@

@@

@@

joined_lm_region_gt <- joined_lm_region %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Region in the US on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))
```

@@

@@

@@

>>>>

# Read in rural income data from
# https://www.ers.usda.gov/data-products/atlas-of-rural-and-small-town-america/
# (United States Department of Agriculture). Might not use it.

@@

# Read in income data for all US Counties from
# https://www.ers.usda.gov/data-products/county-level-data-sets/download-data/
# (US Bureau of Labour Statistics). Might not use it.

@@

# Read in consumer Price Index ata from
# https://www.ers.usda.gov/data-products/food-price-outlook/ (United States
# Department of Agriculture). Might not use it.

@@

anim_save("obesity_shiny/plots/obesity_mean_usmap.gif", plot = last_animation())

@@

ggsave("obesity_shiny/plots/obesity_region_plot.png", plot = last_plot())

@@

ggsave("obesity_shiny/plots/food_poverty_plot.png", plot = last_plot())

@@

ggsave("obesity_shiny/plots/food_lia_plot.png", plot = last_plot())

@@

saveRDS(food_sum, file = "./obesity_shiny/data/food_sum.RDS")

@@

ggsave("obesity_shiny/plots/corr_plot.png", plot = corrplot)

@@

gtsave(joined_lm_age_gt, "age_gt.html")

@@

gtsave(joined_lm_race_gt, "gender_race.html")

@@

gtsave(joined_lm_la_gt, "la_gt.html")

@@

gtsave(joined_lm_urban_gt, "urban_gt.html")

@@

gtsave(joined_lm_poverty_gt, "poverty_gt.html")

@@

joined_lm_region_gt <- joined_lm_region %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Region in the US on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

gtsave(joined_lm_region_gt, "region_gt.html")

@@

# Because there wasn't really any correlation between food access and obesity, I
# thought I'd look at how obesity is affected by poverty. I created a
# scatterplot to reflect that, and choose geom_jitter since many points
# overlapped. Then I drew a best fit line. For the Shiny app, I want to see how
# the different variables affect the mean obesity rate, so I thought I would
# create graphs reflecting each variable. Having x = age is just a sample of my
# code to see if it works, and then I'll allow the user to choose the x variable
# in the Shiny app. Then I saved the plot using ggsave.

@@

ggsave("obesity_shiny/plots/poverty_obesity_plot.png", plot = last_plot())

@@

```{r food access us map}

# I wanted to plot onto a US map food insecurity, so I used plot_usmap. Then I saved it.

lia_usmap <- plot_usmap(data = food_sum, values = "perc_lia", color = "dark green", labels = FALSE) +
    theme(legend.position = "right",
          plot.title = element_text(hjust = 0.5)) + 
    scale_fill_continuous(low = "white", high = "dark green", name = "Percent of Population") +
    labs(title = "Percent of Population (age 18+) Classified as Having Low Income and Low Food Access",
         caption = "Data from USDA and 2010 Census Bureau") +
    theme_void()

ggsave("obesity_shiny/plots/lia_usmap.png", plot = last_plot())

```{r poverty and food access plot}

# I wanted to find the relationship between poverty and food insecurity
# depending on ruralness, so I graphed it. Then I saved it.

poverty_lia_chart <- bootstrap_joined %>% 
  ggplot(aes(x = mean_poverty, y = perc_lia)) +
      geom_jitter(color = "dark green") +
      theme_minimal() +
      theme(panel.grid.minor.y = element_blank(),
            panel.grid.minor.x = element_blank()) +
       labs(title = "Relationship Between Poverty Rate and Low Income and Low Food Access",
            caption = "Data from US Department of Agriculture and 2010 Census Bureau",
            x = "Mean Poverty Rate",
            y = "Percent of Population Classified as \n Having Low Income and Low Food Access") +
       geom_smooth(method = "lm", color = "green")

ggsave("obesity_shiny/plots/poverty_lia_chart.png", plot = last_plot())
